---
title: "Carbon Pools Congo"
author: "Lattifa Fofana, Aimé Kouassi, Eric Forni, Sylvie Gourlet-Fleury & Bruno Hérault"
date: "6/6/2018"
output: 
  github_document:
    toc: true
    toc_depth: 3
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Research Questions
*What is the magnitude of carbon pools in deadwood and small stems as compared to standard AGB (>10 DBH) ?*

*Are there some ecologically-sound relationships between the 3 pools?*

*What is the level of environmental control on pools and relationships?*

# Dead Biomass

```{r DB upload 1, include=FALSE}
c93<-read.csv2("c93.csv",header = TRUE)
c94<-read.csv2("c94.csv",header = TRUE)
c95<-read.csv2("c95.csv",header = TRUE)
c113<-read.csv2("c113.csv",header = TRUE)
c114<-read.csv2("c114.csv",header = TRUE)
c115<-read.csv2("c115.csv",header = TRUE)
c123<-read.csv2("c123.csv",header = TRUE)
c124<-read.csv2("c124.csv",header = TRUE)
c125<-read.csv2("c125.csv",header = TRUE)
c133<-read.csv2("c133.csv",header = TRUE)
c134<-read.csv2("c134.csv",header = TRUE)
c135<-read.csv2("c135.csv",header = TRUE)
c143<-read.csv2("c143.csv",header = TRUE)
c144<-read.csv2("c144.csv",header = TRUE)
c145<-read.csv2("c145.csv",header = TRUE)
c163<-read.csv2("c163.csv",header = TRUE)
c164<-read.csv2("c164.csv",header = TRUE)
c165<-read.csv2("c165.csv",header = TRUE)
c177<-read.csv2("c177.csv",header = TRUE)
c178<-read.csv2("c178.csv",header = TRUE)
c179<-read.csv2("c179.csv",header = TRUE)
c197<-read.csv2("c197.csv",header = TRUE)
c198<-read.csv2("c198.csv",header = TRUE)
c199<-read.csv2("c199.csv",header = TRUE)
c217<-read.csv2("c217.csv",header = TRUE)
c218<-read.csv2("c218.csv",header = TRUE)
c219<-read.csv2("c219.csv",header = TRUE)
c284<-read.csv2("c284.csv",header = TRUE)
c285<-read.csv2("c285.csv",header = TRUE)
c286<-read.csv2("c286.csv",header = TRUE)
c304<-read.csv2("c304.csv",header = TRUE)
c305<-read.csv2("c305.csv",header = TRUE)
c306<-read.csv2("c306.csv",header = TRUE)
c324<-read.csv2("c324.csv",header = TRUE)
c325<-read.csv2("c325.csv",header = TRUE)
c326<-read.csv2("c326.csv",header = TRUE)
lwd<-rbind(c93, c94, c95, c113, c114, c115, c123, c124, c125, c133, c134, c135, 
           c143, c144, c145, c163, c164, c165, c177, c178, c179, c197, c198, c199, c217, 
           c218, c219, c284, c285, c286, c304, c305, c306, c324, c325, c326) # lwd's data combinations = lwd
# rename / arrange some column's name on lwd's data
colnames(lwd)[1]<-"n"
colnames(lwd)[2]<-"x"
lwd$treeID<-paste(lwd$n, lwd$plot, lwd$square, lwd$transect, sep = "_") # creation of treelwdID
# convert to julian date for the new lwd1's data
library(date)
lwd$dateJ<-julian(strptime(lwd$date, "%d/%m/%Y"))
```

```{r DB upload 2, include=FALSE}
d93<-read.csv2("d93.csv",header = TRUE)
d94<-read.csv2("d94.csv",header = TRUE)
d95<-read.csv2("d95.csv",header = TRUE)
d113<-read.csv2("d113.csv",header = TRUE)
d114<-read.csv2("d114.csv",header = TRUE)
d115<-read.csv2("d115.csv",header = TRUE)
d123<-read.csv2("d123.csv",header = TRUE)
d124<-read.csv2("d124.csv",header = TRUE)
d125<-read.csv2("d125.csv",header = TRUE)
d133<-read.csv2("d133.csv",header = TRUE)
d134<-read.csv2("d134.csv",header = TRUE)
d135<-read.csv2("d135.csv",header = TRUE)
d143<-read.csv2("d143.csv",header = TRUE)
d144<-read.csv2("d144.csv",header = TRUE)
d145<-read.csv2("d145.csv",header = TRUE)
d163<-read.csv2("d163.csv",header = TRUE)
d164<-read.csv2("d164.csv",header = TRUE)
d165<-read.csv2("d165.csv",header = TRUE)
d177<-read.csv2("d177.csv",header = TRUE)
d178<-read.csv2("d178.csv",header = TRUE)
d179<-read.csv2("d179.csv",header = TRUE)
d197<-read.csv2("d197.csv",header = TRUE)
d198<-read.csv2("d198.csv",header = TRUE)
d199<-read.csv2("d199.csv",header = TRUE)
d217<-read.csv2("d217.csv",header = TRUE)
d218<-read.csv2("d218.csv",header = TRUE)
d219<-read.csv2("d219.csv",header = TRUE)
d284<-read.csv2("d284.csv",header = TRUE)
d285<-read.csv2("d285.csv",header = TRUE)
d286<-read.csv2("d286.csv",header = TRUE)
d304<-read.csv2("d304.csv",header = TRUE)
d305<-read.csv2("d305.csv",header = TRUE)
d306<-read.csv2("d306.csv",header = TRUE)
d324<-read.csv2("d324.csv",header = TRUE)
d325<-read.csv2("d325.csv",header = TRUE)
d326<-read.csv2("d326.csv",header = TRUE)
swd<-rbind(d93, d94, d95, d113, d114, d115, d123, d124, d125, d133, d134, d135, 
           d143, d144, d145, d163, d164, d165, d177, d178, d179, d197, d198, d199, d217, 
           d218, d219, d284, d285, d286, d304, d305, d306, d324, d325, d326)  # swd's data combinations = swd
# rename / arrange some column's name on swd's data
colnames(swd)[1]<-"n"
colnames(swd)[2]<-"x"
colnames(swd)[3]<-"y"
colnames(swd)[4]<-"circDBH"
colnames(swd)[5]<-"circlow"
colnames(swd)[6]<-"circhigh"
swd$treeID<-paste(swd$n, swd$plot, swd$square, swd$transect, sep = "_") # creation of treelwdID
# convert to julian date for the new lwd1's data
library(date)
swd$dateJ<-julian(strptime(swd$date, "%d/%m/%Y"))
str(swd)
```

## Descriptive Statistics

## Estimating Carbon Pool Values

## Estimating Carbon Pool Variabilities

# Small Stems

```{r SS upload, include=FALSE}

```

## Descriptive Statistics

## Estimating Carbon Pool Values

## Estimating Carbon Pool Variabilities

# AboveGround Biomass

## Results from BIOMASS package

# Linking the 3 carbon pools

## Results

## Discussion


