---
title: "Carbon Pools Congo"
author: "Lattifa Fofana, Aimé Kouassi, Eric Forni, Sylvie Gourlet-Fleury & Bruno Hérault"
date: "6/6/2018"
output: 
  github_document:
    toc: true
    toc_depth: 3
    df_print: paged
---

# Research Questions
*What is the magnitude of carbon pools in deadwood and small stems as compared to standard AGB (>10 DBH) ?*

*Are there some ecologically-sound relationships between the 3 pools?*

*What is the level of environmental control on pools and relationships?*

# Dead Biomass

```{r DB upload 1, include=FALSE}
c93<-read.csv2("c93.csv",header = TRUE)
c94<-read.csv2("c94.csv",header = TRUE)
c95<-read.csv2("c95.csv",header = TRUE)
c113<-read.csv2("c113.csv",header = TRUE)
c114<-read.csv2("c114.csv",header = TRUE)
c115<-read.csv2("c115.csv",header = TRUE)
c123<-read.csv2("c123.csv",header = TRUE)
c124<-read.csv2("c124.csv",header = TRUE)
c125<-read.csv2("c125.csv",header = TRUE)
c133<-read.csv2("c133.csv",header = TRUE)
c134<-read.csv2("c134.csv",header = TRUE)
c135<-read.csv2("c135.csv",header = TRUE)
c143<-read.csv2("c143.csv",header = TRUE)
c144<-read.csv2("c144.csv",header = TRUE)
c145<-read.csv2("c145.csv",header = TRUE)
c163<-read.csv2("c163.csv",header = TRUE)
c164<-read.csv2("c164.csv",header = TRUE)
c165<-read.csv2("c165.csv",header = TRUE)
c177<-read.csv2("c177.csv",header = TRUE)
c178<-read.csv2("c178.csv",header = TRUE)
c179<-read.csv2("c179.csv",header = TRUE)
c197<-read.csv2("c197.csv",header = TRUE)
c198<-read.csv2("c198.csv",header = TRUE)
c199<-read.csv2("c199.csv",header = TRUE)
c217<-read.csv2("c217.csv",header = TRUE)
c218<-read.csv2("c218.csv",header = TRUE)
c219<-read.csv2("c219.csv",header = TRUE)
c284<-read.csv2("c284.csv",header = TRUE)
c285<-read.csv2("c285.csv",header = TRUE)
c286<-read.csv2("c286.csv",header = TRUE)
c304<-read.csv2("c304.csv",header = TRUE)
c305<-read.csv2("c305.csv",header = TRUE)
c306<-read.csv2("c306.csv",header = TRUE)
c324<-read.csv2("c324.csv",header = TRUE)
c325<-read.csv2("c325.csv",header = TRUE)
c326<-read.csv2("c326.csv",header = TRUE)
lwd<-rbind(c93, c94, c95, c113, c114, c115, c123, c124, c125, c133, c134, c135, 
           c143, c144, c145, c163, c164, c165, c177, c178, c179, c197, c198, c199, c217, 
           c218, c219, c284, c285, c286, c304, c305, c306, c324, c325, c326) # lwd's data combinations = lwd
# rename / arrange some column's name on lwd's data
colnames(lwd)[1]<-"n"
colnames(lwd)[2]<-"x"
colnames(lwd)[13]<-"subplot"
lwd$plot<-as.character(lwd$plot)
lwd[lwd$plot=="1 Ouest",]$plot<-"WEST-1"
lwd[lwd$plot=="2 Ouest",]$plot<-"WEST-2"
lwd[lwd$plot=="1 Est",]$plot<-"EAST-1"
lwd[lwd$plot=="2 Est",]$plot<-"EAST-2"
lwd[lwd$subplot == 113 & lwd$transect==3  & lwd$direction==0,]$n=3
lwd[lwd$subplot == 144 & lwd$plot=="EAST-2",]$plot="EAST-1"
# omit value's adding on lwd                                              
lwd= rbind(lwd, c(4,94,0,24.5,23,14.4,5,240,1,0,"17/04/2018","WEST-2",219,2,296.5,"SE"))
lwd= rbind(lwd, c(3,59,0,0,15,7.9,4,245,0,0,"17/04/2018","WEST-2",219,4,116.5,"NO"))
lwd= rbind(lwd, c(9,48,0,0,17,30.5,1,180,1,0,"23/04/2018","WEST-2",179,2,296.5,"SE"))
lwd= rbind(lwd, c(5,79,0,23,22.6,11,3,190,1,0,"17/04/2018","WEST-2",199,2,296.5,"SE"))
lwd= rbind(lwd, c(6,81,0,34,20,10,4,340,1,0,"24/03/2018","WEST-2",178,2,296.5,"SE"))
lwd= rbind(lwd, c(8,50,0,36,37,15.4,3,90,1,0,"06/03/2018","WEST-2",198,1,26.5,"SO"))
lwd= rbind(lwd, c(6,89,0,39,38,9,3,210,1,0,"06/03/2018","WEST-2",198,4,116.5,"NO"))
lwd= rbind(lwd, c(2,56,0,0,42,18,5,150,1,0,"09/03/2018","WEST-2",177,4,116.5,"NO"))
lwd= rbind(lwd, c(7,98,0,23.4,20,11,3,60,0,0,"04/03/2018","WEST-2",197,4,116.5,"NO"))
lwd= rbind(lwd, c(14,100.5,0,0,83,17,5,270,1,0,"13/03/2018","WEST-2",217,3,206.5,"NE"))
lwd= rbind(lwd, c(3,95,0,0,25,33.5,3,30,1,0,"25/04/2018","WEST-1",95,3,206.5,"NE"))
lwd= rbind(lwd, c(4,93,32,0,10.2,24.6,2,300,1,0,"02/03/2018","WEST-1",114,1,26.5,"SO"))
lwd= rbind(lwd, c(3,65,0,0,17,16,4,90,1,0,"10/04/2018","WEST-1",94,3,206.5,"NE"))
lwd= rbind(lwd, c(5,105,0,20,17,9.6,5,70,1,0,"05/03/2018","WEST-1",115,3,206.5,"NE"))
lwd= rbind(lwd, c(14,40,0,22,20,17,5,210,1,0,"05/04/2018","EAST-1",145,1,26.5,"SO"))
lwd= rbind(lwd, c(1,44,0,0,54,14.7,4,300,1,0,"22/03/2018","EAST-1",123,4,116.5,"NO"))
lwd= rbind(lwd, c(5,60,0,20,15,11,1,210,1,0,"21/03/2018","EAST-1",144,1,26.5,"SO"))
lwd= rbind(lwd, c(4,81.5,0,0,23,12,5,280,1,0,"10/03/2018","EAST-2",305,4,116.5,"NO"))
lwd= rbind(lwd, c(5,90,0,0,29,19,3,90,1,0,"07/04/2018","EAST-2",326,2,296.5,"SE"))
#Lwd columns' typology actualisation 
lwd$n=as.numeric(lwd$n)                                                   
lwd$x=as.numeric(lwd$x)
lwd$circumf=as.numeric(lwd$circumf)
lwd$Dh=as.numeric(lwd$Dh)
lwd$Dv=as.numeric(lwd$Dv)
lwd$L=as.numeric(lwd$L)
lwd$decay=as.numeric(lwd$decay)
lwd$trunk=as.numeric(lwd$trunk)
lwd$subplot=as.integer(lwd$subplot)
lwd$transect=as.integer(lwd$transect)
lwd$treeID<-paste(lwd$plot, lwd$subplot, lwd$transect, lwd$n, sep = "_") # creation of treelwdID
# convert to julian date for the new lwd1's data
library(date)
lwd$dateJ<-julian(strptime(lwd$date, "%d/%m/%Y"))
# replace 0's by NA's on lwd$Dh
lwd$Dh[lwd$Dh == 0]= NA
# replace 0's by NA's on lwd$Circumf
lwd$circumf[lwd$circumf == 0]= NA
# calculation of geometric mean diameters Dg   
lwd$Dv[lwd$treeID == "WEST-1_114_4_1"]= lwd$circumf[lwd$treeID == "WEST-1_114_4_1"]/pi
lwd$Dv[lwd$treeID == "WEST-1_114_4_2"]= lwd$circumf[lwd$treeID == "WEST-1_114_4_2"]/pi
lwd$Dv[lwd$treeID == "WEST-1_114_1_1"]= lwd$circumf[lwd$treeID == "WEST-1_114_1_1"]/pi
lwd$Dv[lwd$treeID == "WEST-1_114_1_2"]= lwd$circumf[lwd$treeID == "WEST-1_114_1_2"]/pi
lwd$Dv[lwd$treeID == "WEST-1_114_1_3"]= lwd$circumf[lwd$treeID == "WEST-1_114_1_3"]/pi
lwd$Dg=exp(rowMeans(log(data.frame(lwd$Dh,lwd$Dv)), na.rm=TRUE)) 
```

```{r DB upload 2, include=FALSE}
d93<-read.csv2("d93.csv",header = TRUE)
d94<-read.csv2("d94.csv",header = TRUE)
d95<-read.csv2("d95.csv",header = TRUE)
d113<-read.csv2("d113.csv",header = TRUE)
d114<-read.csv2("d114.csv",header = TRUE)
d115<-read.csv2("d115.csv",header = TRUE)
d123<-read.csv2("d123.csv",header = TRUE)
d124<-read.csv2("d124.csv",header = TRUE)
d125<-read.csv2("d125.csv",header = TRUE)
d133<-read.csv2("d133.csv",header = TRUE)
d134<-read.csv2("d134.csv",header = TRUE)
d135<-read.csv2("d135.csv",header = TRUE)
d143<-read.csv2("d143.csv",header = TRUE)
d144<-read.csv2("d144.csv",header = TRUE)
d145<-read.csv2("d145.csv",header = TRUE)
d163<-read.csv2("d163.csv",header = TRUE)
d164<-read.csv2("d164.csv",header = TRUE)
d165<-read.csv2("d165.csv",header = TRUE)
d177<-read.csv2("d177.csv",header = TRUE)
d178<-read.csv2("d178.csv",header = TRUE)
d179<-read.csv2("d179.csv",header = TRUE)
d197<-read.csv2("d197.csv",header = TRUE)
d198<-read.csv2("d198.csv",header = TRUE)
d199<-read.csv2("d199.csv",header = TRUE)
d217<-read.csv2("d217.csv",header = TRUE)
d218<-read.csv2("d218.csv",header = TRUE)
d219<-read.csv2("d219.csv",header = TRUE)
d284<-read.csv2("d284.csv",header = TRUE)
d285<-read.csv2("d285.csv",header = TRUE)
d286<-read.csv2("d286.csv",header = TRUE)
d304<-read.csv2("d304.csv",header = TRUE)
d305<-read.csv2("d305.csv",header = TRUE)
d306<-read.csv2("d306.csv",header = TRUE)
d324<-read.csv2("d324.csv",header = TRUE)
d325<-read.csv2("d325.csv",header = TRUE)
d326<-read.csv2("d326.csv",header = TRUE)
swd<-rbind(d93, d94, d95, d113, d114, d115, d123, d124, d125, d133, d134, d135, 
           d143, d144, d145, d163, d164, d165, d177, d178, d179, d197, d198, d199, d217, 
           d218, d219, d284, d285, d286, d304, d305, d306, d324, d325, d326)  # swd's data combinations = swd
# rename / arrange some column's name on swd's data
colnames(swd)[1]<-"n"
colnames(swd)[2]<-"x"
colnames(swd)[3]<-"y"
colnames(swd)[13]<-"subplot"
swd$plot<-as.character(swd$plot)
swd[swd$plot=="1 Ouest",]$plot<-"WEST-1"
swd[swd$plot=="2 Ouest",]$plot<-"WEST-2"
swd[swd$plot=="1 Est",]$plot<-"EAST-1"
swd[swd$plot=="2 Est",]$plot<-"EAST-2"
swd[swd$subplot == 144 & swd$plot=="EAST-2",]$plot="EAST-1" 
# creation of treelwdID
swd[swd$subplot == 324 & swd$transect==2  & swd$angle==206.5,]$n=2
swd$treeID<-paste(swd$plot, swd$subplot, swd$transect, swd$n, sep = "_")    # creation of treelwdID
# omit value's adding on swd                                                          #
swd$x[swd$treeID == "EAST-1_145_3_1"]= 29
swd$y[swd$treeID == "EAST-1_145_3_1"]= 7
swd$CIRCdbh[swd$treeID == "EAST-1_145_3_1"]= 205.5
swd$H[swd$treeID == "EAST-1_145_3_1"]= 11.5
swd$decay[swd$treeID == "EAST-1_145_3_1"]= 4
swd$CIRCdbh[swd$treeID == "WEST-1_114_1_1"]= 34
swd$CIRCdbh[swd$treeID == "EAST-2_285_2_1"]= 82
swd$CIRCdbh[swd$treeID == "EAST-2_324_2_1"]= 33
colnames(swd)[4]<-"DBH"
colnames(swd)[5]<-"Dlow"
colnames(swd)[6]<-"Dhigh"
# calculate diameter
swd$DBH=swd$DBH/pi
swd$Dlow=swd$Dlow/pi
swd$Dhigh=swd$Dhigh/pi
# convert to julian date for the new lwd1's data
library(date)
swd$dateJ<-julian(strptime(swd$date, "%d/%m/%Y"))
# replace 0's by NA's on swd
swd$DBH[swd$DBH == 0]= NA
swd$Dlow[swd$Dlow == 0]= NA
swd$Dhigh[swd$Dhigh == 0]= NA
# db's and dt's calculation 
# db
library(dplyr)
DBH = c(swd$DBH)
Dlow = c(swd$Dlow)
test1=tibble(DBH, Dlow )
swd$db<-data.frame(test1 %>% transmute(DBH = ifelse(is.na(DBH), Dlow, DBH)))[,1] 
# dt 
dtDBH=c(1.59*swd$DBH*swd$H^{-0.091})
dtDhigh=c(swd$Dhigh) 
test2=tibble(dtDBH, dtDhigh)
swd$dt<-data.frame(test2 %>% transmute(dtDBH = ifelse(is.na(dtDBH), dtDhigh, dtDBH)))[,1] 
```

## Descriptive Statistics

### Lying Deadwood

#### Density
```{r D density, include=TRUE, echo=FALSE}
library(knitr)
LWD_subplot<-data.frame(subplot=names(table(lwd$subplot)), N=as.numeric(table(lwd$subplot)))
LWD_subplot<-merge(LWD_subplot, unique(data.frame(plot=lwd$plot, subplot=lwd$subplot)), 
                  by.x="subplot", by.y="subplot")
LWD_subplot$N<-(LWD_subplot$N/(4*111.7))*100 # LWD mean values/subplot/100 m

library(ggplot2)
library(devtools)
ggplot(LWD_subplot, aes(N)) + geom_density(aes(fill=factor(plot)), alpha=0.5) + 
  labs(title="Lying deadwood Density Plot", 
       subtitle="Observed Number of lying deadwood per 100m walking, grouped per plot",
       caption="Source: DynAfFor",
       x="Lying deadwood (per 100m walking)",
       fill="# Plot Names")

```

* Hypothesis - A few logging tracks have been seen in WEST plots. More lying deadwoods are expected there.

* Results - No obvious difference between WEST and EAST

* Discussion - The already-seen logging tracks have not impacted large trees.

#### Diameter

```{r DBH distribution, include=TRUE, echo=FALSE}
library(ggplot2)
ggplot(lwd, aes(x = Dg, fill = plot)) +
  geom_histogram(binwidth = 10, alpha = 1, position = "dodge")+
  labs(title="Diameter Distribution of Lying Deadwood", 
       subtitle="Observed Absolute Frequencies grouped per plot",
       caption="Source: DynAfFor",
       x="Diameter (cm)",
       y="Absolute Frequencies",
       fill="# Plot Names")
```

* Hypothesis - In a mature forest, deadwoods are mostly young trees suppressed by competition with large trees

* Results - A somewhat exponential decrease of DBH distribution

* Discussion - We have a mature forest in hand, no obvious difference between plots

#### Length
```{r Length distribution, include=TRUE, echo=FALSE}
library(ggplot2)
ggplot(lwd, aes(x = L, fill = plot)) +
  geom_histogram(binwidth = 3, alpha = 1, position = "dodge")+
  labs(title="Length Distribution of Lying Deadwood", 
       subtitle="Observed Absolute Frequencies grouped per plot",
       caption="Source: DynAfFor",
       x="Length (m)",
       y="Absolute Frequencies",
       fill="# Plot Names")
```

* Hypothesis - In a mature forest, deadwoods are mostly young trees with low heights (lengths) suppressed by competition with large trees

* Results - A somewhat exponential decrease of length (height) distribution

* Discussion - We have a mature forest in hand, no obvious difference between plots

#### Diameter-Length
```{r DBH-Length, include=TRUE, echo=FALSE}
ggplot(lwd, aes(y = L, x = Dg)) + geom_point(aes(color=plot))+
  scale_x_log10()+
  scale_y_log10()+
  geom_smooth(mapping = aes(x = Dg, y = L))+
  labs(title="Length versus Diameter, Lying Deadwood", 
       subtitle="Each point is an individual tree",
       caption="Source: DynAfFor",
       x="Tree Diameter (cm), log-scale",
       y="Tree Length (m), log-scale")
```

* Hypothesis - Because of allometric relationships, we expect a positive correlation between length and DBH

* Results - A weak tendency but a very large variability around this tendency

* Discussion - We have two hypothesis to explain the weak link. (i) Decay rates are not homogeneous along the bole so that we have some parts fully decomposed and other parts almost-intact. This leads to a decoupling between length and DBH. (ii) Many boles/branches were broken at the time of falling. this may explain why we have many short pieces of large DBH

### Standing Deadwood
#### Density

```{r standing density, include=TRUE, echo=FALSE}
library(knitr)
SWD_subplot<-data.frame(subplot=names(table(swd$subplot)), N=as.numeric(table(swd$subplot)))
SWD_subplot<-merge(SWD_subplot, unique(data.frame(plot=swd$plot, subplot=swd$subplot)), 
                   by.x="subplot", by.y="subplot")
Sp= 111.7*20*4-4*20^2
SWD_subplot$N<-SWD_subplot$N/Sp*10000
library(ggplot2)
library(devtools)
ggplot(SWD_subplot, aes(N)) + geom_density(aes(fill=factor(plot)), alpha=0.5) + 
  labs(title="Standing Deadwood Density", 
       subtitle="Observed Number of standing deadwood per hectare, grouped per plot",
       caption="Source: DynAfFor",
       x="Number of standing deadwood (per ha)",
       fill="# Plot Names")
```

* Hypothesis - No difference between blocks/plots

* Results - It seems that there is more standing deadwood on the WEST plots. to be verified with a statistical test (later)

* Discussion - It looks like the WEST forest/plots is more senescent than the EAST forest/plots. We should have a look to the small stems density to verify this hypothesis.

#### DBH
```{r standing DBH, include=TRUE, echo=FALSE}
library(ggplot2)
ggplot(swd, aes(x = db, fill = plot)) +
  geom_histogram(binwidth = 10, alpha = 1, position = "dodge")+
  labs(title="Base diameter (db) Distribution", 
       subtitle="Observed Absolute Frequencies grouped per plot",
       caption="Source: DynAfFor",
       x="Base diameter (cm)",
       y="Absolute Frequencies",
       fill="# Plot Names")
```

* Hypothesis - In a mature forest, deadwoods are mostly young trees suppressed by competition with large trees.

* Results - A somewhat exponential decrease of DBH distribution. Note that in WEST-2, small DBH are over-represented.

* Discussion - We have a mature forest in hand.

#### Height
```{r standing Height, include=TRUE, echo=FALSE}
library(ggplot2)
ggplot(swd, aes(x = H, fill = plot)) +
  geom_density(aes(fill=factor(plot)), alpha=0.5)+
  labs(title="Height Distribution", 
       subtitle="Density curves, grouped per plot",
       caption="Source: DynAfFor",
       x="Height (m)",
       fill="# Plot Names")

```

* Hypothesis - In a mature forest, standing deadwoods are mostly young trees with low heights (lengths) suppressed by competition with large trees

* Results - A somewhat exponential decrease of height distribution

* Discussion - We have a mature forest in hand, no obvious difference between plots

#### Diameter-Height
```{r Height-Diameter, include=TRUE, echo=FALSE}
library(ggplot2)
ggplot(swd, aes(y = H, x = db)) + geom_point(aes(color=plot))  +
    scale_x_log10()+
  scale_y_log10()+
    geom_smooth(mapping = aes(x = db, y = H))+
  labs(title="Height versus Diameter", 
       subtitle="Each point is an individual tree",
       caption="Source: DynAfFor",
       x="Tree Diameter (cm)",
       y="Tree Height (m)")    
```

* Hypothesis - Because of allometric relationships, we expect a positive correlation between length and DBH

* Results - A very weak tendency but a very large variability around this tendency

* Discussion -Many boles/branches were broken at (or after) the time of death. This may explain why we have many short standing boles with large DBH

## Estimating Carbon Pool Values

### Lying Volumes
```{r Lying Volumes, include=TRUE, echo=FALSE}
LWD_subplot<-LWD_subplot[order(as.numeric(as.character(LWD_subplot$subplot))),]
LV <- by(lwd, lwd$subplot, 
    function(x) sum((x$Dg)^2)*pi^2/(8*111.7*4))
LWD_subplot$LV<-as.numeric(unlist(sapply(LV, "[", 1)))

ggplot(LWD_subplot, aes(LV)) + geom_density(aes(fill=factor(plot)), alpha=0.5) + 
  scale_x_log10()+
  labs(title="Distribution of Lying Deadwood Volumes", 
       subtitle="Log-Scaled, grouped per plot",
       caption="Source: DynAfFor",
       x=expression(Volumes~(m3.ha^{-1})),
       fill="# Plot Names")
```

* Hypothesis - A few logging tracks have been seen in WEST plots. More lying deadwood volumes are expected there.

* Results - A subtle difference between WEST and EAST. Not statistically significant.

* Discussion - The already-seen logging tracks have not strongly impacted large trees.

### Standing Volumes
```{r Standing Volumes, include=TRUE, echo=FALSE}
SWD_subplot<-SWD_subplot[order(as.numeric(as.character(SWD_subplot$subplot))),]
SV <- by(swd, swd$subplot, 
    function(x) sum(x$H*((pi*((x$db/100)/2)^2 + pi*((x$dt/100)/2)^2)/2))) / ((4*111.7*20)-(4*20*20)) * 10000

SWD_subplot$SV<-as.numeric(unlist(sapply(SV, "[", 1)))

ggplot(SWD_subplot, aes(SV)) + geom_density(aes(fill=factor(plot)), alpha=0.5) + 
    scale_x_log10()+
  labs(title="Distribution of Standing Deadwood Volumes", 
       subtitle="Log-Scaled, grouped per plot",
       caption="Source: DynAfFor",
       x=expression(Volumes~(m3.ha^{-1})),
       fill="# Plot Names")
```

* Hypothesis - No difference between blocks/plots

* Results - It seems that there is more standing deadwood on the WEST-1 plot. to be verified with a statistical test (later)

* Discussion - These results confirm what we have already seen on the density analysis. It looks like the WEST forest/plots is more senescent than the EAST forest/plots. We should have a look to the small stems density to verify this hypothesis.

### Standing versus Lying Volumes

```{r StandingLying Density, include=TRUE, echo=FALSE}
WD<-data.frame(plot=LWD_subplot$plot, subplot=LWD_subplot$subplot,
               N_lv=LWD_subplot$N, V_lv=LWD_subplot$LV, 
               N_sv=SWD_subplot$N, V_sv=SWD_subplot$SV)

ggplot(WD, aes(x = N_sv, y = N_lv)) +
         geom_smooth(mapping = aes(x = N_sv, y = N_lv))+
        geom_point(shape = 15, size  = 4, aes( color=plot))+
        labs(title="Lying versus Standing Deadwood Densities", 
         subtitle="Standing per ha, Lying per 100m walking",
         caption="Source: DynAfFor",
         x="Number of standing deadwood (per ha)",
         y="Number of lying deadwood (per 100m walking)")
```

* Hypothesis 1 - All plots have similar maturity levels. In this case, we do expect no relationships between standing and lying deadwoods OR a negative relationships if total volumes remain stable and standing/lying compensate each other.

* Hypothesis 2 - Plots have different maturity levels. In this case, we do expect a positive relationship between standing and lying deadwoods with LOW standing/lying values for young patches and HIGH  standing/lying values for senescent patches.

* Results - No obvious correlation. A tiny tendency for negative relationships.

* Discussion - All plots have similar maturity levels.

```{r StandingLying Volumes, include=TRUE, echo=FALSE}

ggplot(WD, aes(x = V_sv, y = V_lv)) +
    scale_x_sqrt()+
  scale_y_sqrt()+
    geom_smooth(mapping = aes(x = V_sv, y = V_lv))+
   geom_point(shape = 15, size  = 4, aes(color=plot))+

        labs(title="Lying versus Standing Deadwood Volumes", 
         subtitle="Volumes per ha, grouped per plot",
         caption="Source: DynAfFor",
         x=expression(Standing_Volumes~(m3.ha^{-1})),
         y=expression(Lying_Volumes~(m3.ha^{-1})))
```

* Hypothesis 1 - All plots have similar maturity levels. In this case, we do expect no relationships between standing and lying deadwoods OR a negative relationships if total volumes remain stable and standing/lying compensate each other.

* Hypothesis 2 - Plots have different maturity levels. In this case, we do expect a positive relationship between standing and lying deadwoods with LOW standing/lying values for young patches and HIGH  standing/lying values for senescent patches.

* Results - No correlation at all. 

* Discussion - It looks like standing and lying volumes are ramdomly distributed.

## Estimating Carbon Pool Variabilities


# Small Stems

```{r SS upload, include=FALSE}
tig1=read.csv2("ti1.csv")
tig2=read.csv2("ti2.csv")
tig3=read.csv2("ti3.csv")
tig4=read.csv2("ti4.csv")
tig5=read.csv2("ti5.csv")
tig5$X<-NULL
tig6=read.csv2("ti6.csv")
tig7=read.csv2("ti7.csv")
tig8=read.csv2("ti8.csv")
tig9=read.csv2("ti9.csv")
tig10=read.csv2("ti10.csv")
tig11=read.csv2("ti11.csv")
tig12=read.csv2("ti12.csv")
tig13=read.csv2("ti13.csv")
tig14=read.csv2("ti14.csv")
tig15=read.csv2("ti15.csv")
tig16=read.csv2("ti16.csv")
tig17=read.csv2("ti17.csv")
tig18=read.csv2("ti18.csv")
tig19=read.csv2("ti19.csv")
tig20=read.csv2("ti20.csv")
tig21=read.csv2("ti21.csv")
tig22=read.csv2("ti22.csv")
tig23=read.csv2("ti23.csv")
tig24=read.csv2("ti24.csv")
tig25=read.csv2("ti25.csv")
tig26=read.csv2("ti26.csv")
tig27=read.csv2("ti27.csv")
tig28=read.csv2("ti28.csv")
tig29=read.csv2("ti29.csv")
tig30=read.csv2("ti30.csv")
tig31=read.csv2("ti31.csv")
tig32=read.csv2("ti32.csv")
tig33=read.csv2("ti33.csv")
tig34=read.csv2("ti34.csv")
tig35=read.csv2("ti35.csv")
tig36=read.csv2("ti36.csv")
tig37=read.csv2("ti37.csv")
tig38=read.csv2("ti38.csv")
tig39=read.csv2("ti39.csv")
tig40=read.csv2("ti40.csv")
tig41=read.csv2("ti41.csv")
tig42=read.csv2("ti42.csv")
tig43=read.csv2("ti43.csv")
tig44=read.csv2("ti44.csv")
tig45=read.csv2("ti45.csv")
tig46=read.csv2("ti46.csv")
tig47=read.csv2("ti47.csv")
tig48=read.csv2("ti48.csv")
colnames(tig10)[9]="DBH"
tabx<-rbind(tig1,tig2, tig3, tig4,tig5,tig6,tig7,tig8,tig9,tig10,tig11,tig12,tig13,tig14,tig15,tig16,tig17,tig18,tig19,tig20,tig21,tig22,tig23,tig24,tig25,tig26,tig27,tig28,tig29,tig30,tig31,tig32,tig33,tig34,tig35,tig36,tig37,tig38,tig39,tig40,tig41,tig42,tig43,tig44,tig45,tig46,tig47,tig48)
colnames(tabx)[2]="plot"
colnames(tabx)[3]="subplot"
colnames(tabx)[4]="n"
colnames(tabx)[5]="vernacularname"
colnames(tabx)[2]="plot"
colnames(tabx)[6]="g"
colnames(tabx)[7]="sp"
colnames(tabx)[8]="h"
colnames(tabx)[10]="quadrat"
tabx$treeID<-paste(tabx$plot, tabx$subplot, tabx$quadrat, tabx$n, sep = "_")
tabx$dateJ<-julian(strptime(tabx$DATE, "%d/%m/%Y"))
tabx$plot<-as.character(tabx$plot)
tabx[tabx$plot=="1 ouest",]$plot<-"WEST-1"
tabx[tabx$plot=="2 ouest",]$plot<-"WEST-2"
tabx[tabx$plot=="2 OUEST",]$plot<-"WEST-2"
tabx[tabx$plot=="2 Est",]$plot<-"EAST-2"
tabx[tabx$plot=="2 EST",]$plot<-"EAST-2"
tabx[tabx$plot=="1 EST",]$plot<-"EAST-1"
tabx[tabx$plot=="1 OUEST",]$plot<-"WEST-1"
tabx[tabx$plot=="1 OESUT",]$plot<-"WEST-1"
```

## Descriptive Statistics

### Stem Density

```{r DS_SS, include=TRUE, echo=FALSE}
library(knitr)
SS_quadrat<-data.frame(subplot=names(table(tabx$subplot)), N=as.numeric(table(tabx$subplot)))
SS_quadrat[SS_quadrat$subplot %in% c(114, 144, 198, 305),]$N<-SS_quadrat[SS_quadrat$subplot %in% c(114, 144, 198, 305),]$N/4
SS_quadrat<-merge(SS_quadrat, unique(data.frame(plot=tabx$plot, subplot=tabx$subplot)), by.x="subplot", by.y="subplot")
SS_quadrat$N<-SS_quadrat$N/400*10000
library(ggplot2)
library(devtools)
g <- ggplot(SS_quadrat, aes(N))
g + geom_density(aes(fill=factor(plot)), alpha=0.5) + 
    labs(title="Small Stem Density Plot", 
         subtitle="Observed Absolute Frequencies grouped per plot",
         caption="Source: DynAfFor",
         x="N Small Stems (per ha)",
         fill="# Plot Names")
```

* Hypothesis - Similar maturity levels, no difference between block/plots.

* Results - No obvious difference. On average 5000 stem/ha.

* Discussion - Similar maturity levels. The number of small stems is more than 10 times the number of DBH>10 trees.

### DBH Distribution

```{r DBH_SS, include=TRUE, echo=FALSE}
library(ggplot2)
ggplot(tabx, aes(x = DBH, fill = plot)) +
        geom_histogram(binwidth = 0.5, alpha = 1, position = "dodge")+
      labs(title="DBH Distribution", 
         subtitle="Observed Absolute Frequencies grouped per plot",
         caption="Source: DynAfFor",
         x="DBH (cm)",
         y="Absolute Frequencies",
         fill="# Plot Names")
```

* Hypothesis - In a mature forest, we expect a negative exponential distribution

* Results - A somewhat exponential decrease of DBH distribution

* Discussion - We have a mature forest in hand, no obvious difference between plots

### Height Distribution

```{r HEIGHT_SS, include=TRUE, echo=FALSE}
library(ggplot2)
ggplot(tabx, aes(x = h, fill = plot)) +
        geom_histogram(binwidth = 0.5, alpha = 1, position = "dodge")+
      labs(title="Height Distribution", 
         subtitle="Observed Absolute Frequencies grouped per plot",
         caption="Source: DynAfFor",
         x="Height (m)",
         y="Absolute Frequencies",
         fill="# Plot Names")
```

* Hypothesis - In a mature forest, we expect a negative exponential distribution

* Results - A somewhat exponential decrease of height distribution

* Discussion - We have a mature forest in hand, no obvious difference between plots

### Basic Correlations

```{r SS dbh height, include=TRUE, echo=FALSE, comment=FALSE}
library(ggplot2)
ggplot(data = tabx) +
  geom_point(mapping = aes(x = DBH, y = h, color=plot)) +
  geom_smooth(mapping = aes(x = DBH, y = h))+
      labs(title="Height versus DBH", 
         subtitle="Each point is an individual tree",
         caption="Source: DynAfFor",
         x="DBH (cm",
         y="Height (m)",
         fill="# Plot Names")

```

* Hypothesis - Because of allometric relationships, we expect a positive correlation between height and DBH

* Results - A positive and significant relationship

* Discussion - Allometric relationship verified, can be used, in the future, to infer small_stem_AGB when height not available.

## Estimating Carbon Pool Values

```{r agb SS, include=TRUE, echo=FALSE}
library(BIOMASS)
library(ggplot2)
HDmodelSS <- modelHD(D = tabx$DBH, H = tabx$h, method="log2", drawGraph = TRUE)
#test<-correctTaxo(tabx$g, tabx$sp, score = 0.5)
wsgSS<-getWoodDensity(tabx$g,tabx$sp, stand=tabx$subplot)
tabx$wsg<-wsgSS$meanWD
tabx$wsgSD<-wsgSS$sdWD
#resultMCss <- by(tabx, tabx$subplot, 
#    function(x) AGBmonteCarlo(D = x$DBH, WD = x$wsg, errWD = x$wsgSD, 
#    HDmodel = HDmodelSS, Dpropag = "chave2004", n=1000))
#save(resultMCss, file="resultMCss.RData")
load("resultMCss.RData")
SS_quadrat$subplot<-as.numeric(as.character(SS_quadrat$subplot))
SS_quadrat<-SS_quadrat[order(SS_quadrat$subplot),]
SS_quadrat$AGB<- as.numeric(unlist(sapply(resultMCss, "[", 1)))
SS_quadrat$AGB_low<-sapply(sapply(resultMCss, "[", 4), function (x) x[1])
SS_quadrat$AGB_high<-sapply(sapply(resultMCss, "[", 4), function (x) x[2])
# correct for subplot with 4 quadrats
SS_quadrat[SS_quadrat$subplot %in% c(114,144,198,305),]$AGB<-SS_quadrat[SS_quadrat$subplot %in% c(114,144,198,305),]$AGB/4
SS_quadrat[SS_quadrat$subplot %in% c(114,144,198,305),]$AGB_low<-SS_quadrat[SS_quadrat$subplot %in% c(114,144,198,305),]$AGB_low/4
SS_quadrat[SS_quadrat$subplot %in% c(114,144,198,305),]$AGB_high<-SS_quadrat[SS_quadrat$subplot %in% c(114,144,198,305),]$AGB_high/4
SS_quadrat$AGB<-SS_quadrat$AGB/400*10000
SS_quadrat$AGB_low<-SS_quadrat$AGB_low/400*10000
SS_quadrat$AGB_high<-SS_quadrat$AGB_high/400*10000
SS_quadrat$subplot<-as.factor(SS_quadrat$subplot)
ggplot(SS_quadrat, aes(x = subplot, y = AGB, color=plot)) +
   geom_errorbar(aes(ymin = AGB_low,
                     ymax = AGB_high),
                     width = 0.05, 
                     size  = 0.5) +
   geom_point(shape = 15, size  = 4)+
        labs(title="Small Stems Biomass Distribution", 
         subtitle="Estimated with BIOMASS package and full error propagation",
         caption="Source: DynAfFor",
         x="Subplot Number",
         y=expression(AGB~(Mg.ha^{-1}))) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```

* Hypothesis - From the literature analysis, we expect that the small stem biomass will be no more than 5-10% of the total biomass

* Results - Small stem biomass in our subplot is between 10 and 20 T/ha. No obvious difference between plots.

* Discussion - Assuming a total AGB between 300-400 T/ha, the proportion of this biomass is about 2.5-5% of the total AGB. Very low!

## Estimating Carbon Pool Variabilities

# AboveGround Biomass

## Basic Checks

```{r lound data, include=TRUE, echo=FALSE, warning=FALSE}
library(ggplot2)
loun <- read.csv("~/Library/Mobile Documents/com~apple~CloudDocs/Bruno/Publications/Congo/Congo/analyses/Loun.csv")
loun$bloc_parcelle<-as.character(loun$bloc_parcelle)
loun[loun$bloc_parcelle=="bloc est/parcelle 1",]$bloc_parcelle<-"EAST-1"
loun[loun$bloc_parcelle=="bloc est/parcelle 2",]$bloc_parcelle<-"EAST-2"
loun[loun$bloc_parcelle=="bloc ouest/parcelle 1",]$bloc_parcelle<-"WEST-1"
loun[loun$bloc_parcelle=="bloc ouest/parcelle 2",]$bloc_parcelle<-"WEST-2"
ggplot(loun, aes(x = diametre_camp2, color=bloc_parcelle)) +
        geom_histogram(binwidth = 0.05, alpha = 1)+
      labs(title="DBH Distribution", 
         subtitle="Observed Absolute Frequencies, squared-root scale on x_axis",
         caption="Source: DynAfFor",
         x="DBH (cm)",
         y="Absolute Frequencies")+scale_x_sqrt()+ facet_wrap(~bloc_parcelle)
```

```{r wsg, include=TRUE, echo=FALSE, warning=FALSE}
library(BIOMASS)
loun$genus<-sapply(strsplit(as.character(loun$nom_scientifique_valid), "\\s+"), function (x) x[1])
loun$species<-sapply(strsplit(as.character(loun$nom_scientifique_valid), "\\s+"), function (x) x[2])
wsg<-getWoodDensity(loun$genus,loun$species, stand=loun$carre)
loun$wsg<-wsg$meanWD
loun$wsgSD<-wsg$sdWD
ggplot(loun, aes(x = wsg, color=bloc_parcelle)) +
        geom_histogram(binwidth = 0.05, alpha = 1)+
      labs(title="Wood Density Distribution", 
         subtitle="Observed Absolute Frequencies",
         caption="Source: DynAfFor",
         x="WSG (g.cm^-3)",
         y="Absolute Frequencies")+ facet_wrap(~bloc_parcelle)
```

## Results from BIOMASS package

```{r agb, include=TRUE, echo=FALSE}
library(BIOMASS)
library(ggplot2)
HDmodel <- modelHD(D = loun$diametre_camp2, H = loun$hauteur_camp2/10, method = "weibull")
#resultMC <- by(loun, loun$carre, 
#    function(x) AGBmonteCarlo(D = x$diametre_camp2, WD = x$wsg, errWD = x$wsgSD, 
#    HDmodel = HDmodel, Dpropag = "chave2004", n=1000))
#save(resultMC, file="resultMC.RData")
load("resultMC.RData")
plot<-data.frame(unique(data.frame(plot=lwd$plot, subplot=lwd$subplot)))
plot$subplot<-as.factor(plot$subplot)
plot$AGB<- as.numeric(unlist(sapply(resultMC, "[", 1)))
plot$AGB_low<-sapply(sapply(resultMC, "[", 4), function (x) x[1])
plot$AGB_high<-sapply(sapply(resultMC, "[", 4), function (x) x[2])
ggplot(plot, aes(x = subplot, y = AGB, color=plot)) +
   geom_errorbar(aes(ymin = AGB_low,
                     ymax = AGB_high),
                     width = 0.05, 
                     size  = 0.5) +
   geom_point(shape = 15, size  = 4)+
        labs(title="AboveGround Biomass Distribution", 
         subtitle="Estimated with BIOMASS package and full error propagation",
         caption="Source: DynAfFor",
         x="Subplot Number",
         y=expression(AGB~(Mg.ha^{-1}))) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
ggplot(plot, aes(AGB)) + geom_density(aes(fill=factor(plot)), alpha=0.5, bw=20) + 
  labs(title="AboveGround Biomass Density per Plot", 
       subtitle="Estimated with BIOMASS package and full error propagation",
       caption="Source: DynAfFor",
       x=expression(AGB~(Mg.ha^{-1})),
       fill="# Plot Names")
```


# Linking the 3 carbon pools together
## Small Stems versus Large Stems
```{r ss vs ls, include=TRUE, echo=FALSE}
data<-plot
SS_quadrat1<-SS_quadrat
SS_quadrat1$plot<-NULL
SS_quadrat1$AGBss_low<-SS_quadrat1$AGB_low
SS_quadrat1$AGB_low<-NULL
SS_quadrat1$AGBss_high<-SS_quadrat1$AGB_high
SS_quadrat1$AGB_high<-NULL
SS_quadrat1$AGBss<-SS_quadrat1$AGB
SS_quadrat1$AGB<-NULL
data<-merge(plot, SS_quadrat1, by.x="subplot", by.y="subplot")
ggplot(data, aes(x = AGB, y = AGBss)) +
    geom_smooth(mapping = aes(x = AGB, y = AGBss))+
  geom_errorbar(aes(ymin = AGBss_low,
                     ymax = AGBss_high,
                     xmin = AGB_low,
                     xmax = AGB_high, color=plot),
                     width = 0.05, 
                     size  = 0.5) +
   geom_point(shape = 15, size  = 4, aes(color=plot))+
        labs(title="Small versus Large Stems Biomass", 
         subtitle="Estimated with BIOMASS package and full error propagation",
         caption="Source: DynAfFor",
         x=expression(Large_Stem_AGB~(Mg.ha^{-1})),
         y=expression(Small_Stem_AGB~(Mg.ha^{-1})))
```
